\begin{rubric}{Experience}
\entry*[\textbf{2018.3 -- now}]%
	\textbf{Internet of Things and Intelligent Systems Lab,BUPT.\qquad }%
\entry*[\textbf{2018.3 -- now}]%
		\textbf{Autonomous navigation robot system}%
\text{\qquad This robot system can autonomously navigate in a outdoor environment and give warning when it \par \qquad detect someone nearby.}\par
\text{\qquad  Responsible for Visual SLAM module, which use a binocular camera to reconstruct the 3D environmental \par \qquad information.}\par
\text{\qquad  Responsible for people detection, which use deep learning to process video stream from the camera.}\par
\text{\qquad  Responsible for remote control on web page which use ROS-Bridge and rSSH.}\par
\entry*[\textbf{2017.10 -- 2018.1}]%
\textbf{Course Projcet}
\entry*[\textbf{2017.10 -- 2018.1}]%
\textbf{Extend OS Frame for VxWorks}%
\text{\qquad Responsible for optimizing memory management.}\par
\text{\qquad Using variable-length memory pool design reduces internal and external fragmentation when \par \qquad memory is allocated.}\par
\entry*[\textbf{2016.11 -- 2017.2}]%
	\textbf{Software Engineering Institute Lab,WHU.}%
\entry*[\textbf{2016.11 -- 2017.2}]%
	\textbf{Ocean oil ship exploration system}%
\text{\qquad Responsible for parsing XML file and optimizing matrix operation by C++.}\par
\text{\qquad Implement a universal function to parse XML file by recursive method.}\par
\text{\qquad Optimize sparse matrix multiplication which has 3 times better performance. }
\end{rubric}